\section{Related Work}\label{related_work}
Graph alignment is used to solve a large variety of real world problems. \cite{singh2008isorank} aligns proteins across multiple biological networks, using both graph structure and node similarity scores, making it an example of using \textit{restricted} graph alignment to solve real problems. \cite{kazemi2015growing} presents an algorithm to identify users across social networks based on a set of pre-aligned nodes, which can be perceived as node features. \cite{zhang2016final} presents a general purpose graph alignment algorithm \textsc{Final}, that takes advantage of edge and node attributes, and shows that edge and node information can compliment graph topology in finding an alignment. While edge and node attributes can be useful for solving real problems, \textit{unrestricted} algorithms are often able to be modified to take advantage of edge and node attributes and allows researchers to better compare different algorithms.\\

The \textit{mediated} graph alignment approach has been the predominant paradigm in recent literature. Notable algorithms employing this approach include \textsc{CONE} \citep{chen2020cone}, which utilizes Graph Neural Networks to compute node embeddings, and \textsc{REGAL} \citep{heimann2018regal}, which learns embeddings based on graph structure. \textsc{GRAAL} \cite{kuchaiev2010topological} leverages frequent patterns in graphs, while \textsc{GRASP} \citep{hermanns2021grasp} and \textsc{LREA} \citep{nassar2018low} use spectral analysis. A comprehensive evaluation by \cite{skitsas2023GAEval} examines a wide range of state-of-the-art graph alignment algorithms, all classified as mediated according to the definition by \cite{fugal2024}. The study shows significant variance in the accuracy and ranking of these algorithms, depending on the specific graph and noise level.\\

Accelerating graph algorithms using GPUs is a widely studied technique. A survey by \cite{shi2018graph} gives an overview of a wide array of algorithms and techniques used to adapt algorithms to GPU hardware. Also the problem of graph alignment has been explored on GPUs. We are aware of two examples, \textsc{cuAlign} \citep{xiang2023cualign} and \textsc{SLOTAlign} \citep{tang2023robust}, both of which uses GPUs to scale graph alignment to larger graphs.